EDA

### 2018-09-07 contest/eda/eda.Rmd
kayla small edits

---
title: "EDA"
author: "The Competent Ones"
date: "August 4, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(devtools)
library(deuce)
library(knitr)
devtools::load_all("..") # Loads courtsports package
```

@@

# Create data for Grand Slam finals
gsf = filter(pbp, !qual & (wim | french | us | aus))
```
```{r numbers}
dim(gsf)
colnames(gsf)
kable(table(gsf$tny_name))

>>>>

---
title: "EDA"
author: "The Competent Ones"
date: "August 4, 2018"
output: 
  html_document:
    toc:  true
    toc_float:  true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)

```{r libraries}
library(devtools)
library(deuce)
library(knitr)
# devtools::load_all("..") # Loads courtsports package
```

@@

# Create data for Grand Slam finals
gsf = filter(pbp, !qual & (wim | french | us | aus))
```

```{r numbers}
dim(gsf)
colnames(gsf)
kable(table(gsf$tny_name))
